---
title: "ASD Electrogustometry Report - DRAFT"
author: "Paul D Allen"
date: '`r date()`'
output: html_document
---
### About this document
```{r,  echo=FALSE, include=FALSE}
require(rmarkdown)
require(ggplot2)
require(aod)
require(stats)
library("psyphy", lib.loc="C:/Program Files/R/R-3.1.2/library")
library("knitr", lib.loc="C:/Program Files/R/R-3.1.2/library")

#SURFACE 
#dataDir = 'C:/Users/paul allen/Dropbox/@ Across-Site work tools/ASD/_Data Analysis Taste-Smell/Taste Smell Data/Completed EG Files (notepad)'
#filedir = 'C:/Users/paul allen/Dropbox/@R-working/gustometry'
#source('C:/Users/paul allen/Dropbox/@R-working/gustometry/gustometerData.R')
#ENT
#dataDir = 'C:/Users/pallen/Dropbox/@ Across-Site work tools/ASD/_Data Analysis Taste-Smell/Taste Smell Data/Completed EG Files (notepad)'
#filedir = 'C:/Users/pallen/Dropbox/@R-working/gustometry'
#source('C:/Users/pallen/Dropbox/@R-working/gustometry/gustometerData.R')

### DNP Lab
dataDir = 'S:/Research/BennettoLab/TSFB Study/Data/Cleaned data/Electrogustometry'
filedir = 'C:/Users/pallen/Desktop/Dropbox/@R-working/gustometry'
notefile = 'gustonotes20141001.txt'
demofile = 'DemoEG.csv'
gustnotes <-  read.delim(paste(sep = "", collapse = NULL, filedir, '/', notefile), stringsAsFactors=FALSE)
DemoEG <- read.csv("C:/Users/pallen/Desktop/Dropbox/@R-working/gustometry/DemoEG.csv")
gustnotes$note <- paste(gustnotes$Note1, gustnotes$Note2, gustnotes$Note3)
gustnotes$ID <- paste('TS', gustnotes$Idnum, gustnotes$Idletter, sep ="")
DemoEG$type <- paste(DemoEG$OrdName, DemoEG$Group, sep ="_")

source('C:/Users/pallen/Desktop/Dropbox/@R-working/gustometry/gustometerData.R')
# define link function 

allFiles = dir(dataDir, pattern ="*.txt")
numStamps = rep(NA,length(allFiles))
for (i in 1:length(allFiles)) {
  fileName <- paste(dataDir,"/",allFiles[i], sep='')
  numStamps[i] <- length(gustometerData(fileName, timeStamps = TRUE))
  }
timeStampData = data.frame(
  id = allFiles,
  ntimes = numStamps
  )
SID <- substr(allFiles, start = 7, stop = 13)
gender <- rep(NA, length(SID))
age <- rep(NA, length(SID))
group <- rep(NA, length(SID))
L_logThresh <- rep(NA, length(SID))
L_logprob <- rep(NA, length(SID))
R_logThresh <- rep(NA, length(SID))
R_logprob <- rep(NA, length(SID))
L_revThresh <- rep(NA, length(SID))
R_revThresh <- rep(NA, length(SID))
L_allRevs <- rep(NA, length(SID))
R_allRevs <- rep(NA, length(SID))
chiSqr <- rep(NA, length(SID))
GuessAll <- rep(NA, length(SID))
guessLeft <- rep(NA, length(SID))
guessRight <- rep(NA, length(SID))
propLeft <- rep(NA, length(SID))
pLeft <- rep(NA, length(SID))
propRight <- rep(NA, length(SID))
pRight <- rep(NA, length(SID))
pchi <- rep(NA, length(SID))
Rratio <- rep(NA, length(SID))
bias <- rep(NA, length(SID))
biasRept <- rep(NA, length(SID))
note <- rep(NA, length(SID))
demonote <- rep(NA, length(SID))

summaryData <- data.frame(SID,gender,age,group,chiSqr,pchi,GuessAll,Rratio,bias,biasRept,R_logThresh,R_logprob,R_allRevs,R_revThresh,propRight,pRight,guessRight,L_logThresh,L_logprob,L_revThresh,L_allRevs,propLeft,pLeft,guessLeft, note, demonote)
```


This document compiles the current electogustometry data in a format that will allow rapid evaluation of the data from each subject.

It is important to be able to at a glace see the Right and Left track information, and then also the logistic regression estimates on this data.

We want to be able to also compare the threshold estimates from reversals and regression and whether subjects are likely guessing or biased in their responses.

---

\pagebreak


## Subject Data

```{r, echo = FALSE, include=FALSE,warning=FALSE}
out = NULL
numtoanalyse = length(allFiles)
for (i in 1:numtoanalyse) {
  thisNote <- gustnotes$note[gustnotes$ID == SID[i]]
  thisNote <- paste(thisNote, collapse="; ")
  if (length(thisNote)==0) {thisNote = 'No note in the database!'}
  summaryData$note[i] <- thisNote
  
  thisGender <- as.character(DemoEG$Gender[DemoEG$SID == SID[i]])
  if (length(thisGender)==0) {thisGender = 'NA'}  
  summaryData$gender[i] <- thisGender
  
  thisAge <- DemoEG$Age[DemoEG$SID == SID[i]]
  if (length(thisAge)==0) {thisAge = 'NA'} 
  summaryData$age[i] <- thisAge
  
  thisGroup <- DemoEG$type[DemoEG$SID == SID[i]]
  if (length(thisGroup)==0) {thisGroup = 'NA'} 
  summaryData$group[i] <- thisGroup
  
  summaryData$demonote[i] <- paste(DemoEG$Note[DemoEG$SID == SID[i]], collapse="; ")
  if (numStamps[i] != 2) {
    out = c(out, c('Skip file ', allFiles[i]), 'Note:', thisNote, '---')}
  else {
    out = c(out,knit_child('gustoreport.Rmd'))
    }
  }

write.csv(summaryData, file = paste('EG_SummaryData_Draft_',Sys.Date(),".csv", sep = ''))

summaryData$L_logThresh[summaryData$L_logThresh < -6] <- -10
summaryData$R_logThresh[summaryData$R_logThresh < -6] <- -10
summaryData$L_logThresh[summaryData$L_logThresh > 36] <- 40
summaryData$R_logThresh[summaryData$R_logThresh > 36] <- 40

summaryData$L_revThresh[summaryData$L_revThresh < -6] <- -10
summaryData$R_revThresh[summaryData$R_revThresh < -6] <- -10
summaryData$L_revThresh[summaryData$L_revThresh > 36] <- 40
summaryData$R_revThresh[summaryData$R_revThresh > 36] <- 40

summaryData$L_allRevs[summaryData$L_allRevs < -6] <- -10
summaryData$R_allRevs[summaryData$R_allRevs < -6] <- -10
summaryData$L_allRevs[summaryData$L_allRevs > 36] <- 40
summaryData$R_allRevs[summaryData$R_allRevs > 36] <- 40


```
`r paste(out ,collapse = '\n')`




### Summary of Electrogustometry data

Obtained track data from `r length(summaryData$L_revThresh)-sum(is.na(summaryData$L_revThresh))` out of `r length(summaryData$L_revThresh)` records.

The `r sum(is.na(summaryData$L_revThresh))` subjects with problematic tracks are:
`r summaryData$SID[is.na(summaryData$L_revThresh)]`

\pagebreak


## Histograms and Correlations (or lack of...)
# Chi-Square
Large chi-square indicates responses matched the stimuli
It's a metric of how well the subject 'got it'

``` {r, echo=FALSE, fig.height=5, fig.width=5}

hist(summaryData$chiSqr)

```
\pagebreak

# Logistic

``` {r, echo=FALSE, fig.height=3.5, fig.width=3.5}

hist(summaryData$L_logThresh, breaks = -10:40)

hist(summaryData$R_logThresh, breaks = -10:40)

plot(summaryData$L_logThresh,summaryData$R_logThresh,xlab="Left Logistic Fit Threshold (dB)",ylab="Right Logistic Fit Threshold (dB)", main = 'Comparision of Left and Right - Logistic Fit') 
lin <- function(x) x
curve(lin, from = -10, to = 40, add = TRUE)
```

\pagebreak


# Reversals
```{r, echo= FALSE, fig.height=3.5, fig.width=3.5}

hist(summaryData$L_revThresh, breaks = -10:40)

hist(summaryData$R_revThresh, breaks = -10:40)

plot(summaryData$L_revThresh,summaryData$R_revThresh,xlab="Left Reversal Threshold (dB)",ylab="Right Reversal Threshold Threshold (dB)", main = 'Comparision of Left and Right - Reversal Threshold') 
curve(lin, from = -10, to = 40, add = TRUE)
```


\pagebreak

# All reverals

```{r, echo= FALSE, fig.height=3.5, fig.width=3.5}


hist(summaryData$L_allRevs, breaks = -10:40)

hist(summaryData$R_allRevs, breaks = -10:40)

plot(summaryData$L_allRevs,summaryData$R_allRevs,xlab="Left Reversal Threshold (dB)",ylab="Right Reversal Threshold Threshold (dB)", main = 'Comparision of Left and Right - All Reversal Average') 
curve(lin, from = -10,to = 40, add = TRUE)


```
