### Subject `r substr(allFiles[i],7,13)` Electrogustometry Report

```{r, echo=FALSE,warning=FALSE}
#Behind the scenes
fileName <- paste(dataDir,"/",allFiles[i], sep='')
trialTracks <- gustometerData(fileName)

# Responding at chance Calculation
nLeft <- sum(trialTracks$Stim == 'L')
corLeft <- sum(trialTracks$corr[trialTracks$Stim == 'L'])
#minL <- min(trialTracks$track[trialTracks$Stim == 'L'])
lastL <- trialTracks$track[trialTracks$Stim == 'L'][length(trialTracks$track[trialTracks$Stim == 'L'])]
nRight <- sum(trialTracks$Stim == 'R')
corRight <- sum(trialTracks$corr[trialTracks$Stim == 'R'])
#minR <- min(trialTracks$track[trialTracks$Stim == 'R'])
lastR <- trialTracks$track[trialTracks$Stim == 'R'][length(trialTracks$track[trialTracks$Stim == 'R'])]
fractionLR <- nLeft/(nLeft+nRight)
rLeft <- sum(trialTracks$Resp == 'L')
rRight <- sum(trialTracks$Resp == 'R')
# these go to the binomial tests below

#Left Side
leftT <- trialTracks$track[trialTracks$Stim == "L"]
leftD <- rep(0,length(leftT))
for (j in 2:length(leftT)){
  if (leftT[j]<leftT[j-1]) {
    leftD[j] <- -1
    } else if (leftT[j]>leftT[j-1]) {
      leftD[j] <- 1
      } else {leftD[j] <- leftD[j-1]}
  }

leftD[length(leftD)+1] <- -trialTracks$corr[trialTracks$Stim == "L"][length(leftD)]
revL <- rep(NA,6)
k = 1
for (j in 2:length(leftD)){
  if (abs(leftD[j]-leftD[j-1])==2) {
    revL[k] = leftT[j-1]
    k<- k+1
    }
  }

xdatL <- c(trialTracks$track[trialTracks$Stim =='L'],-20, 50)
ydatL <- c(trialTracks$corr[trialTracks$Stim =='L'],0,1)

levs <- sort(unique(xdatL))
correct <- rep(0, length(levs))
incorrect <- rep(0, length(levs))
fraction <- rep(0, length(levs))

for (j in 1:length(levs)) {
  correct[j] <- sum(ydatL[xdatL == levs[j]])
  incorrect[j] <- sum(1-ydatL[xdatL == levs[j]])
  fraction[j] <- correct[j] /(correct[j] +incorrect[j])
  }

datL <- as.data.frame(cbind(levs,correct,incorrect,fraction))
gLeft <- glm(cbind(correct, incorrect) ~ levs,family=binomial(mafc.logit(2)),datL)

pLogL <- with(gLeft, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))

#Right Side
rightT <- trialTracks$track[trialTracks$Stim == "R"]
rightD <- rep(0,length(rightT))

for (j in 2:length(rightT)){
  if (rightT[j]<rightT[j-1]) {
    rightD[j] <- -1
    } else if (rightT[j]>rightT[j-1]) {
      rightD[j] <- 1
      } else {rightD[j] <- rightD[j-1]}
  }
rightD[length(rightD)+1] <- -trialTracks$corr[trialTracks$Stim == "R"][length(rightD)]
revR <- rep(NA,6)
k = 1
for (j in 2:length(rightD)){
  if (abs(rightD[j]-rightD[j-1])==2) {
    revR[k] = rightT[j-1]
    k<- k+1
    }
  }

xdatR <- c(trialTracks$track[trialTracks$Stim =='R'], -20, 50)
ydatR <- c(trialTracks$corr[trialTracks$Stim =='R'], 0, 1)

levs <- sort(unique(xdatR))
correct <- rep(0, length(levs))
incorrect <- rep(0, length(levs))
fraction <- rep(0, length(levs))
for (j in 1:length(levs)) {
  correct[j] <- sum(ydatR[xdatR == levs[j]])
  incorrect[j] <- sum(1-ydatR[xdatR == levs[j]])
  fraction[j] <- correct[j] /(correct[j] +incorrect[j])
  }

datR <- as.data.frame(cbind(levs,correct,incorrect,fraction))
gRight <- glm(cbind(correct, incorrect) ~ levs,family=binomial(mafc.logit(2)),datR)

pLogR <- with(gRight, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))

if (is.na(mean(revR[3:6],na.rm = TRUE))) {
  revR <- rep(lastR,6)
}

if (is.na(mean(revL[3:6],na.rm = TRUE))) {
  revL <- rep(lastL,6)
}

biasp <- binom.test(c(rLeft, rRight), p = fractionLR)
if (biasp$p.value < 0.05) {
  biasResp <- "biased"
} else {biasResp <- "not biased"}

levels(trialTracks$Stim) <- c("Stim L", "Stim R")
levels(trialTracks$Resp) <- c("Resp L", "Resp R")

chisqr<- chisq.test(table(trialTracks$Stim,trialTracks$Resp))
                   
summaryData$chiSqr[i] <- chisqr$statistic
summaryData$pchi[i] <- chisqr$p.value
summaryData$Rratio[i] <- rRight/(rLeft + rRight)
summaryData$bias[i] <- biasp$p.value
summaryData$biasRept[i] <- biasResp

summaryData$L_logThresh[i] <- -coef(gLeft)[1] / coef(gLeft)[2]
summaryData$L_logprob[i] <- pLogL
if (pLogL < 0.05) {
  L_ThresSig = "sig"} else { L_ThresSig = "not sig"}
summaryData$L_revThresh[i] <- mean(revL[3:6],na.rm = TRUE)
summaryData$L_allRevs[i] <- mean(revL,na.rm = TRUE)

summaryData$R_logThresh[i] <-  -coef(gRight)[1] / coef(gRight)[2]
summaryData$R_logprob[i] <- pLogR
if (pLogR < 0.05) {
  R_ThresSig = "sig"} else { R_ThresSig = "not sig"}
summaryData$R_revThresh[i] <- mean(revR[3:6],na.rm = TRUE)
summaryData$R_allRevs[i] <- mean(revR,na.rm = TRUE)

if (is.na(chisqr$p.value)) {
  GuessAll <- "fully biased"
} else if (chisqr$p.value < 0.05) {
  GuessAll <- "not guessing"
} else {
  GuessAll <- "maybe guessing!"
  if (chisqr$statistic < 1) {GuessAll <- "surely guessing"}
  }

Leftbinomial <- binom.test(corLeft, nLeft, 0.5)
if (Leftbinomial$p.value < 0.05) {
  guessLeft <- "not guessing"
} else {
  guessLeft <- "guessing"
  optimal <- binom.test(corLeft, nLeft, 0.666)
  if (optimal$p.value > 0.05) {guessLeft <- "2D-1U optimal"}
  }

Rightbinomial <- binom.test(corRight, nRight, 0.5)
if (Rightbinomial$p.value < 0.05) {
  guessRight <- "not guessing"
} else {
  guessRight <- "guessing"
  optimal <- binom.test(corRight, nRight, 0.666)
  if (optimal$p.value > 0.05) {guessRight <- "2D-1U optimal"}
  }

summaryData$GuessAll[i] <- GuessAll
summaryData$propLeft[i] <- corLeft/nLeft
summaryData$guessLeft[i] <- guessLeft

summaryData$pLeft[i] <- Leftbinomial$p.value
summaryData$propRight[i] <- corRight/nRight
summaryData$guessRight[i] <- guessRight
summaryData$pRight[i] <- Rightbinomial$p.value
```


```{r, results="asis", echo=FALSE}
kable(table(trialTracks$Resp,trialTracks$Stim))
#table(trialTracks$Stim,trialTracks$Resp)
#chisq.test(table(trialTracks$Stim,trialTracks$Resp))
#Leftbinomial <- binom.test(corLeft, nLeft, 0.5)
#Rightbinomial <- binom.test(corRight, nRight, 0.5)
```

**Chi-Square for both tracks is `r chisqr$statistic`, so this subject is `r GuessAll` (p = `r chisqr$p.value`)**

**The subject's response ratio was `r rRight/(rLeft + rRight)*100`% Right and so probably `r biasResp` (p = `r biasp$p.value`)**

**Note on session: `r thisNote`**

**Note on subject: `r summaryData$demonote[i]`**


```{r, echo = FALSE, fig.height=2.8, fig.width=3.5}

plot(1:length(rightT),rightT, xlab = "Right Side Trial Number", ylab = "Electrogustometer Level", ylim = c(-10,40), main = 'Right Side Track')

lines(c(1,length(rightT)),c(summaryData$R_allRevs[i],summaryData$R_allRevs[i]), col = "black", lty = 1)
lines(c(1,length(rightT)),c(summaryData$R_revThresh[i],summaryData$R_revThresh[i]), col = "black", lty = 2)
lines(c(1,length(rightT)),c(summaryData$R_logThresh[i],summaryData$R_logThresh[i]), col = "red")

plot(datR$levs,datR$fraction,xlab="Stim Level (dB)",ylab="Fraction Correct", main = 'Right Side Track Logistic Fit',ylim=c(0,1), xlim= c(datR$levs[2]-1, datR$levs[length(datR$levs)-1]+1)) 

curve(predict(gRight,data.frame(levs=x),type="resp"),add=TRUE,col = "red")
lines(c(summaryData$R_allRevs[i],summaryData$R_allRevs[i]),c(0,1), col = "black", lty = 1)
lines(c(summaryData$R_revThresh[i],summaryData$R_revThresh[i]),c(0,1), col = "black", lty = 2)
lines(c(summaryData$R_logThresh[i],summaryData$R_logThresh[i]),c(0,1), col = "red")
```

* The proportion correct was `r corRight/nRight` and the exact binomial test suggests that this subject is `r guessRight` (p = `r Rightbinomial$p.value`)
* The 75% point of the logistic regression is `r summaryData$R_logThresh[i]` dB and the fit is `r R_ThresSig`nificanctly different to a flat line.
* The average of all reversals is `r summaryData$R_allRevs[i]` dB.
* The average of the trimmed reversals is `r summaryData$R_revThresh[i]` dB.

```{r, echo = FALSE,fig.height=2.8, fig.width=3.5}
plot(1:length(leftT),leftT, xlab = "Left Side Trial Number", ylab = "Electrogustometer Level", ylim = c(-10,40), main = 'Left Side Track')

lines(c(1,length(leftT)),c(summaryData$L_allRevs[i],summaryData$L_allRevs[i]), col = "black", lty = 1)
lines(c(1,length(leftT)),c(summaryData$L_revThresh[i],summaryData$L_revThresh[i]), col = "black", lty = 2)
lines(c(1,length(leftT)),c(summaryData$L_logThresh[i],summaryData$L_logThresh[i]), col = "blue")

plot(datL$levs,datL$fraction,xlab="Stim Level (dB)",ylab="Fraction Correct", main = 'Left Side Track Logistic Fit',ylim=c(0,1),xlim= c(datL$levs[2]-1,datL$levs[length(datL$levs)-1]+1) )

curve(predict(gLeft,data.frame(levs=x),type="resp"),add=TRUE, col = "blue")
lines(c(summaryData$L_allRevs[i],summaryData$L_allRevs[i]), c(0,1),col = "black", lty = 1)
lines(c(summaryData$L_revThresh[i],summaryData$L_revThresh[i]), c(0,1),col = "black", lty = 2)
lines(c(summaryData$L_logThresh[i],summaryData$L_logThresh[i]), c(0,1),col = "blue")

```

* The proportion correct was `r corLeft/nLeft` and the exact binomial test suggests that this subject is `r guessLeft` (p = `r Leftbinomial$p.value`)
* The 75% point of the logistic regression is `r summaryData$L_logThresh[i]` dB and the fit is `r L_ThresSig`nificanctly different to a flat line.
* The average of all reversals is `r mean(revL,na.rm = TRUE)` dB.
* The average of the trimmed reversals is `r mean(revL[3:6],na.rm = TRUE)` dB.

---

\pagebreak

