### Subject `r substr(allFiles[i],3,7)` Smell Threshold Report

```{r, echo=FALSE,warning=FALSE}
#Behind the scenes
fileName <- paste(dataDir,"/",allFiles[i], sep='')
thisDate <- as.numeric(file.info(fileName)$mtime)/24/3600+25569
trialTracks <- smellData(fileName)

track <- trialTracks$track
baseline <- trialTracks$thresh[2]

startAnalysis <- which(track == baseline)[1]

if (-2 %in% track) {ceilingFlag <- TRUE; cfText <- '**WARNING track hits ceiling**'} else {ceilingFlag <- FALSE; cfText <- ''}
if (-10 %in% track) {floorFlag <- TRUE; ffText <- 'NB track hits floor'} else {floorFlag <- FALSE; ffText <-''}

nTrack <- length(trialTracks$track)

# this gets the data ready for the probit fit
xdat <- c(track[startAnalysis:nTrack],-12, 0)
ydat <- c(trialTracks$corr[startAnalysis:nTrack],0,1)

levs <- sort(unique(xdat))
correct <- rep(0, length(levs))
incorrect <- rep(0, length(levs))
fraction <- rep(0, length(levs))

for (j in 1:length(levs)) {
  correct[j] <- sum(ydat[xdat == levs[j]])
  incorrect[j] <- sum(1-ydat[xdat == levs[j]])
  fraction[j] <- correct[j] /(correct[j] +incorrect[j])
}

dat <- as.data.frame(cbind(levs,correct,incorrect,fraction))
g <- glm(cbind(correct, incorrect) ~ levs,family=binomial(mafc.logit(2)),dat)

pLog <- with(g, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))

# Add here the bias calculation and responding at chance Calculation
nFirst <- sum(trialTracks$stim[startAnalysis:nTrack] == 'Odor')
nSecond <- sum(trialTracks$stim[startAnalysis:nTrack] == 'Blank')

rFirst <- sum(trialTracks$resp[startAnalysis:nTrack] == 'First')
rSecond <- sum(trialTracks$resp[startAnalysis:nTrack] == 'Second')

fractionFS<- nFirst/(nFirst+nSecond)
biasp <- binom.test(c(rFirst, rSecond), p = fractionFS)
if (biasp$p.value < 0.05) {
  biasResp <- "biased"
} else {biasResp <- "not biased"}

levels(trialTracks$stim) <- c("Blank", "Odor")
levels(trialTracks$resp) <- c("First", "Second")

chisqr<- chisq.test(table(trialTracks$stim[startAnalysis:nTrack],trialTracks$resp[startAnalysis:nTrack]))
#                    
summaryData$chiSqr[i] <- chisqr$statistic
summaryData$pchi[i] <- chisqr$p.value
summaryData$Rratio[i] <- rFirst/(rFirst + rSecond)
summaryData$bias[i] <- biasp$p.value
summaryData$biasRept[i] <- biasResp
summaryData$ceilingFlag[i] <- ceilingFlag
summaryData$floorFlag[i] <- floorFlag
summaryData$trackLength[i] <- nTrack
summaryData$baseline[i] <- baseline
summaryData$lastfour[i] <- mean(trialTracks$track[(nTrack-3):nTrack])

summaryData$sst_temp[i] <- as.character(trialTracks$info[5])
summaryData$sst_age[i] <- as.character(trialTracks$info[9])

thresh <- trialTracks$thresh[1]

# sometimes Threshold is incorrectly positive (this is because of the geo mean)
if (thresh > 0) {thresh <- -thresh}
threshTrack <- trialTracks$thresh[3:length(trialTracks$thresh)]
threshTrack <- threshTrack[is.na(threshTrack) == F]
nRevs <- length(threshTrack)
summaryData$spread[i] <- sd(threshTrack[(nRevs-4):nRevs])

logThresh <- -coef(g)[1] / coef(g)[2]

summaryData$logThresh[i] <- logThresh
summaryData$logprob[i] <- pLog
summaryData$threshdiff[i] <- logThresh-thresh

if (pLog < 0.05) {
  ThresSig = "sig"} else { ThresSig = "not sig"}
summaryData$thresh[i] <- thresh

if (is.na(chisqr$p.value)) {
  GuessAll <- "fully biased"
} else if (chisqr$p.value < 0.05) {
  GuessAll <- "not guessing"
} else {
  GuessAll <- "maybe guessing!"
  if (chisqr$statistic < 1) {GuessAll <- "surely guessing"}
}

summaryData$GuessAll[i] <- GuessAll

### ALGORITHM for checking Smell Threshold
# 1)	Chi square < 1, 'surely guessing', set Thresh = -1.5
# 2)	Logistic fit with threshold <=-10, set Thresh = -10.5
# 3)	Track threshold -10, set Thresh to -10.5; -2 set Thresh to -1.5
# 4)	Reverals SD <= 0.5, set Thresh to track threshold
# 5)	logistic fit  good (p<0.1) and difference between logistic and track threshold is less than 1dB,  set Thresh to track threshold
# 6)	Remainder set thresh to mean of last four trials
if (chisqr$statistic < 1) {
  algo_thresh <- -1.5
  algo_stage <- 'Chi square less than 1.'
} else if (logThresh <= -10) {
  algo_thresh <- -10.5
  algo_stage <- 'Responses better than -10.'
} else if (thresh == -2) {
  algo_thresh <- -1.5
  algo_stage <- 'Responses worse than -2.'
} else if (summaryData$spread[i] <= 0.5) {
  algo_thresh <- thresh
  algo_stage <- 'Reversals are very tight.'
} else if (pLog < 0.1 & abs(summaryData$threshdiff[i]) < 1) {
  algo_thresh <- thresh
  algo_stage <- 'Psych function and Track Agree.'
} else {
  algo_thresh <- summaryData$lastfour[i]
  algo_stage <- 'Last Four trials describes best.'
}

summaryData$algo_thresh[i] <- algo_thresh
summaryData$algo_type[i] <- algo_stage

```

Table of Stimulus in 1st interval vs Response of which interval contained odor after start of baseline
```{r, results="asis", echo=FALSE}
kable(table(trialTracks$stim[startAnalysis:nTrack],trialTracks$resp[startAnalysis:nTrack]))
```

* Blank-Second & Odor-First are correct responses, Blank-First & Odor-Second are incorrect responses
```{r, echo = FALSE, fig.height=2.8, fig.width=3.5}
plot(1:nTrack,track, col=trialTracks$corr+2, xlab = "Trial Number", ylab = "Smell Level", ylim = c(-11,-1), main = 'Track')

lines(c(1,nTrack),c(thresh,thresh), col = "black", lty = 1)
lines(c(1,nTrack),c(logThresh, logThresh), col = "red")
lines(c(startAnalysis,startAnalysis),c(-2, -10), col = "green")
lines(c(nTrack-5,nTrack),c(algo_thresh,algo_thresh), col = "blue", lwd = 3, lty = 2)


plot(dat$levs,dat$fraction,xlab="Stim Level",ylab="Fraction Correct", main = 'Track Logistic Fit',ylim=c(0,1), xlim= c(dat$levs[2]-1, dat$levs[length(dat$levs)-1]+1)) 

curve(predict(g,data.frame(levs=x),type="resp"),add=TRUE,col = "red")
lines(c(thresh,thresh),c(0,1), col = "black", lty = 1)
lines(c(logThresh,logThresh),c(0,1), col = "red")
lines(c(algo_thresh,algo_thresh),c(0,1), col = "blue", lwd = 3, lty = 2)
```

* Baseline was established at `r baseline` dB, with threshold `r sprintf("%.1f",thresh)` dB
* The Algorithm suggests a threshold of `r sprintf("%.1f",algo_thresh)` dB because `r algo_stage`

* Chi-Square for the track is `r sprintf("%.1f",chisqr$statistic)`, so this subject is `r GuessAll` (p = `r sprintf("%.3f",chisqr$p.value)`)
* From the responses we can estimate a ``r sprintf("%.1f",(1-chisqr$p.value)*100)``% chance that the subject is responding to the stimulus.
* The subject's response ratio was `r sprintf("%.1f",rFirst/(rFirst + rSecond)*100)`% first-interval and so probably `r biasResp` (p = `r sprintf("%.3f",biasp$p.value)`)

* The 75% point of the logistic regression on the track after baseline is `r sprintf("%.1f",logThresh)` dB and the fit is `r ThresSig`nificantly different to a flat line.

* The length of the track is `r nTrack` trials. `r cfText` `r ffText`

* Note on subject: `r demonote`

---

\pagebreak

