### Subject `r substr(allFiles[i],3,7)` Smell Threshold Report

```{r, echo=FALSE,warning=FALSE}
#Behind the scenes
fileName <- paste(dataDir,"/",allFiles[i], sep='')
trialTracks <- smellData(fileName)

track <- trialTracks$track
nTrack <- length(trialTracks$track)

# this gets the data ready for the probit fit
xdat <- c(track,-20, 50)
ydat <- c(trialTracks$corr,0,1)

levs <- sort(unique(xdat))
correct <- rep(0, length(levs))
incorrect <- rep(0, length(levs))
fraction <- rep(0, length(levs))

for (j in 1:length(levs)) {
  correct[j] <- sum(ydat[xdat == levs[j]])
  incorrect[j] <- sum(1-ydat[xdat == levs[j]])
  fraction[j] <- correct[j] /(correct[j] +incorrect[j])
  }

dat <- as.data.frame(cbind(levs,correct,incorrect,fraction))
g <- glm(cbind(correct, incorrect) ~ levs,family=binomial(mafc.logit(2)),dat)

pLog <- with(g, pchisq(null.deviance - deviance, df.null - df.residual, lower.tail = FALSE))

# Add here the bias calculation and responding at chance Calculation
nFirst <- sum(trialTracks$stim == 'Odor')
nSecond <- sum(trialTracks$stim == 'Blank')

rFirst <- sum(trialTracks$resp == 'First')
rSecond <- sum(trialTracks$resp == 'Second')

fractionFS<- nFirst/(nFirst+nSecond)
 biasp <- binom.test(c(rFirst, rSecond), p = fractionFS)
 if (biasp$p.value < 0.05) {
   biasResp <- "biased"
 } else {biasResp <- "not biased"}
 
 levels(trialTracks$stim) <- c("Blank", "Odor")
 levels(trialTracks$resp) <- c("First", "Second")
 
 chisqr<- chisq.test(table(trialTracks$stim,trialTracks$resp))
#                    
 summaryData$chiSqr[i] <- chisqr$statistic
 summaryData$pchi[i] <- chisqr$p.value
 summaryData$Rratio[i] <- rFirst/(rFirst + rSecond)
 summaryData$bias[i] <- biasp$p.value
 summaryData$biasRept[i] <- biasResp

thresh <- trialTracks$thresh[1]
# sometimes Threshold is incorrectly positive (this is because of the geo mean)
if (thresh > 0) {thresh <- -thresh}
threshTrack <- trialTracks$thresh[3:length(trialTracks$thresh)]
threshTrack <- threshTrack[is.na(threshTrack) == F]
nRevs <- length(threshTrack)
if (nRevs > 3){
summaryData$arithThresh[i] <- mean(threshTrack[(nRevs-4):nRevs])
summaryData$geoThresh[i] <- -exp(mean(log(abs(threshTrack[(nRevs-4):nRevs]))))
} else {
  summaryData$arithThresh[i] <- 0
  summaryData$geoThresh[i] <- 0
  }

logThresh <- -coef(g)[1] / coef(g)[2]

summaryData$logThresh[i] <- logThresh
summaryData$logprob[i] <- pLog

if (pLog < 0.05) {
  ThresSig = "sig"} else { ThresSig = "not sig"}
summaryData$Thresh[i] <- thresh

 if (is.na(chisqr$p.value)) {
   GuessAll <- "fully biased"
} else if (chisqr$p.value < 0.05) {
  GuessAll <- "not guessing"
} else {
  GuessAll <- "maybe guessing!"
  if (chisqr$statistic < 1) {GuessAll <- "surely guessing"}
  }

summaryData$GuessAll[i] <- GuessAll

```


```{r, results="asis", echo=FALSE}
 kable(table(trialTracks$resp,trialTracks$stim))
#table(trialTracks$stim,trialTracks$resp)
#chisq.test(table(trialTracks$stim,trialTracks$resp))
#Leftbinomial <- binom.test(corLeft, nLeft, 0.5)
#Rightbinomial <- binom.test(corRight, nRight, 0.5)
```
 
**Chi-Square for both tracks is `r chisqr$statistic`, so this subject is `r GuessAll` (p = `r chisqr$p.value`)**

**The subject's response ratio was `r rFirst/(rFirst + rSecond)*100`% First and so probably `r biasResp` (p = `r biasp$p.value`)**
 
**Note on session: `r thisNote`**

**Note on subject: `r summaryData$demonote[i]`**
 
 
```{r, echo = FALSE, fig.height=2.8, fig.width=3.5}

plot(1:nTrack,track, xlab = "Trial Number", ylab = "Smell Level", ylim = c(-10,0), main = 'Track')

lines(c(1,nTrack),c(thresh,thresh), col = "black", lty = 1)
lines(c(1,nTrack),c(logThresh, logThresh), col = "red")

plot(dat$levs,dat$fraction,xlab="Stim Level",ylab="Fraction Correct", main = 'Track Logistic Fit',ylim=c(0,1), xlim= c(dat$levs[2]-1, dat$levs[length(dat$levs)-1]+1)) 

curve(predict(g,data.frame(levs=x),type="resp"),add=TRUE,col = "red")
lines(c(thresh,thresh),c(0,1), col = "black", lty = 1)
lines(c(logThresh,logThresh),c(0,1), col = "red")
```

* The 75% point of the logistic regression is `r logThresh` dB and the fit is `r ThresSig`nificanctly different to a flat line.
* The geometric mean threshold is `r thresh` dB, while the arithmetic mean threshold is `r summaryData$arithThresh[i]` dB.

---

\pagebreak

