---
title: "ASD Smell Threshold Report - DRAFT"
author: "Paul D Allen"
date: '`r date()`'
output: html_document
---
### About this document
```{r,  echo=FALSE, include=FALSE}
require(rmarkdown)
require(ggplot2)
require(aod)
require(stats)
library("psyphy")
library("knitr")
library("xlsx")

#ENT 
dataDir = 'X:/Research/BennettoLab/TSFB Study/Data/Cleaned data/Smell Threshold Data Files'
filedir = 'X:/Research/BennettoLab/TSFB Study/Data/Cleaned data'
source('C:/Users/pallen/Documents/GitHub/R_TSFB/smellData.R')

notefile = 'notesEGST_2016_02_05.xlsx'
demofile = 'DemoEG_2016_02_05.xlsx'

gustnotes <-  read.xlsx(paste(sep = "", collapse = NULL, filedir, '/', notefile),1)
DemoEG <-  read.xlsx(paste(sep = "", collapse = NULL, filedir, '/', demofile),1)

gustnotes$ID <- paste('TS', gustnotes$FamilyID, gustnotes$MemberID, sep ="")
DemoEG$type <- paste(DemoEG$OrdName, DemoEG$Group, sep ="_")

#local ENT
#dataDir = 'C:/Users/pallen/Dropbox/@ Across-Site work tools/ASD/_Data Analysis Taste-Smell/Taste Smell Data/Completed EG Files (notepad)'
#filedir = 'C:/Users/pallen/Dropbox/@R-working/gustometry'
#source('C:/Users/pallen/Dropbox/@R-working/gustometry/gustometerData.R')

### DNP Lab
# dataDir = 'S:/Research/BennettoLab/TSFB Study/Data/Cleaned data/Smell Thresholds'
# filedir = 'C:/Users/pallen/Desktop/Dropbox/@R-working/gustometry'
# notefile = 'gustonotes20141001.txt'
# demofile = 'DemoEG.csv'
# gustnotes <-  read.delim(paste(sep = "", collapse = NULL, filedir, '/', notefile), stringsAsFactors=FALSE)
# DemoEG <- read.csv("C:/Users/pallen/Desktop/Dropbox/@R-working/gustometry/DemoEG.csv")
# gustnotes$note <- paste(gustnotes$Note1, gustnotes$Note2, gustnotes$Note3)
# gustnotes$ID <- paste('TS', gustnotes$Idnum, gustnotes$Idletter, sep ="")
# DemoEG$type <- paste(DemoEG$OrdName, DemoEG$Group, sep ="_")
# 
# source('C:/Users/pallen/Desktop/Dropbox/@R-working/gustometry/smellData.R')

# define link function 

allFiles = dir(dataDir, pattern ="*.xls")
#numStamps = rep(NA,length(allFiles))
# for (i in 1:length(allFiles)) {
#   fileName <- paste(dataDir,"/",allFiles[i], sep='')
#   numStamps[i] <- length(gustometerData(fileName, timeStamps = TRUE))
#   }
# timeStampData = data.frame(
#   id = allFiles
#   #ntimes = numStamps
#   )
SID <- substr(allFiles, start = 1, stop = 7)
gender <- rep(NA, length(SID))
age <- rep(NA, length(SID))
group <- rep(NA, length(SID))
logThresh <- rep(NA, length(SID))
logprob <- rep(NA, length(SID))
Thresh <- rep(NA, length(SID))
chiSqr <- rep(NA, length(SID))
GuessAll <- rep(NA, length(SID))
 arithThresh <- rep(NA, length(SID))
 geoThresh <- rep(NA, length(SID))
# propLeft <- rep(NA, length(SID))
# pLeft <- rep(NA, length(SID))
# propRight <- rep(NA, length(SID))
# pRight <- rep(NA, length(SID))
 pchi <- rep(NA, length(SID))
 Rratio <- rep(NA, length(SID))
 bias <- rep(NA, length(SID))
 biasRept <- rep(NA, length(SID))
 ceilingFlag <- rep(NA, length(SID))
 floorFlag <- rep(NA, length(SID))
 trackLength <- rep(NA, length(SID))
note <- rep(NA, length(SID))
demonote <- rep(NA, length(SID))
thisDate <- rep(NA, length(SID))
baseline <- rep(NA, length(SID))
spread <- rep(NA, length(SID))
lastfour <- rep(NA, length(SID))

sst_id<- rep(NA, length(SID))
 sst_dob <- rep(NA, length(SID))
 sst_temp <- rep(NA, length(SID))
 sst_testdate <- rep(NA, length(SID))
 sst_age <- rep(NA, length(SID))
 sst_dur <- rep(NA, length(SID))

#summaryData <- data.frame(SID,gender,age,group,chiSqr,pchi,GuessAll,Rratio,bias,biasRept,R_logThresh,R_logprob,R_allRevs,R_revThresh,propRight,pRight,guessRight,L_logThresh,L_logprob,L_revThresh,L_allRevs,propLeft,pLeft,guessLeft, note, demonote)
summaryData <- data.frame(SID,sst_id,sst_dob,gender,age,sst_age,group,thisDate,sst_testdate,sst_dur,chiSqr,pchi,GuessAll,Rratio,bias,biasRept,baseline, spread, lastfour,logThresh,logprob,Thresh,arithThresh, geoThresh,ceilingFlag, floorFlag,trackLength, note, demonote)
#summaryData <- data.frame(SID,gender,age,group,logThresh,logprob,Thresh, note, demonote)

```


This document compiles the current Smell Threshold data in a format that will allow rapid evaluation of the data from each subject.

It is important to be able to at a glace see the track information, and then also the logistic regression estimates on this data.

We want to be able to also compare the threshold estimates from reversals and regression and whether subjects are likely guessing or biased in their responses.

---

\pagebreak


## Subject Data

```{r, echo = FALSE, include=FALSE,warning=FALSE}
out = NULL
numtoanalyse = length(allFiles)
for (i in 1:numtoanalyse) {
  thisNote <- gustnotes$STTadminNotes[gustnotes$ID == SID[i]]
 # thisNote <- paste(thisNote, collapse="; ")
  if (length(thisNote)==0) {thisNote = 'No note in the database!'}
  summaryData$note[i] <- thisNote
  
  thisGender <- as.character(DemoEG$Gender[DemoEG$SID == SID[i]])
  if (length(thisGender)==0) {thisGender = 'NA'}  
  summaryData$gender[i] <- thisGender
  
  thisAge <- DemoEG$Age[DemoEG$SID == SID[i]]
  if (length(thisAge)==0) {thisAge = 'NA'} 
  summaryData$age[i] <- thisAge
  
  thisGroup <- DemoEG$type[DemoEG$SID == SID[i]]
  if (length(thisGroup)==0) {thisGroup = 'NA'} 
  summaryData$group[i] <- thisGroup
  
 summaryData$demonote[i] <- paste(DemoEG$Note[DemoEG$SID == SID[i]], collapse="; ")
 # summaryData$demonote[i] <- DemoEG$Note[DemoEG$SID == SID[i]]
  
  #if (numStamps[i] != 2) {
#     out = c(out, c('Skip file ', allFiles[i]), 'Note:', thisNote, '---')}
#   else {
    out = c(out,knit_child('smellthreshold.Rmd'))
#     }
  }

write.csv(summaryData, file = paste('ST_SummaryData_Draft_',Sys.Date(),".csv", sep = ''))

# summaryData$L_logThresh[summaryData$L_logThresh < -6] <- -10
# summaryData$R_logThresh[summaryData$R_logThresh < -6] <- -10
# summaryData$L_logThresh[summaryData$L_logThresh > 36] <- 40
# summaryData$R_logThresh[summaryData$R_logThresh > 36] <- 40
# 
# summaryData$L_revThresh[summaryData$L_revThresh < -6] <- -10
# summaryData$R_revThresh[summaryData$R_revThresh < -6] <- -10
# summaryData$L_revThresh[summaryData$L_revThresh > 36] <- 40
# summaryData$R_revThresh[summaryData$R_revThresh > 36] <- 40
# 
# summaryData$L_allRevs[summaryData$L_allRevs < -6] <- -10
# summaryData$R_allRevs[summaryData$R_allRevs < -6] <- -10
# summaryData$L_allRevs[summaryData$L_allRevs > 36] <- 40
# summaryData$R_allRevs[summaryData$R_allRevs > 36] <- 40


```
`r paste(out ,collapse = '\n')`




### Summary of Smell Threshold data

Obtained track data from `r length(summaryData$arithThresh)-sum(is.na(summaryData$arithThresh))` out of `r length(summaryData$arithThresh)` records.

The `r sum(is.na(summaryData$arithThresh))` subjects with problematic tracks are:
`r summaryData$SID[is.na(summaryData$arithThresh)]`

\pagebreak


## Histograms and Correlations (or lack of...)
# Chi-Square
Large chi-square indicates responses matched the stimuli
It's a metric of how well the subject 'got it'

``` {r, echo=FALSE, fig.height=5, fig.width=5}

hist(summaryData$chiSqr)

```
\pagebreak

# Logistic

``` {r, echo=FALSE, fig.height=3.5, fig.width=3.5}

hist(summaryData$logThresh)#, breaks = -10:-2)

#hist(summaryData$R_logThresh, breaks = -10:40)

# plot(summaryData$logThresh,summaryData$R_logThresh,xlab="Left Logistic Fit Threshold (dB)",ylab="Right Logistic Fit Threshold (dB)", main = 'Comparision of Left and Right - Logistic Fit') 
# lin <- function(x) x
# curve(lin, from = -10, to = 40, add = TRUE)
```

\pagebreak


# Reversals
```{r, echo= FALSE, fig.height=3.5, fig.width=3.5}

hist(summaryData$Thresh, breaks = -10:-2)

# hist(summaryData$R_revThresh, breaks = -10:40)
# 
# plot(summaryData$L_revThresh,summaryData$R_revThresh,xlab="Left Reversal Threshold (dB)",ylab="Right Reversal Threshold Threshold (dB)", main = 'Comparision of Left and Right - Reversal Threshold') 
# curve(lin, from = -10, to = 40, add = TRUE)
```


\pagebreak


```
