```{r, echo=FALSE,warning=FALSE}
  if (i<10) {numstr <- paste("0",as.character(i), sep ="")
  } else {numstr <- as.character(i)}
```
  
# Taste Responses to Taste Strip number `r numstr` : `r tastelist[i]` level `r as.character(levellist[i])`
```{r, echo = FALSE, fig.height=2.8, fig.width=3.5}
  data <- na.omit(eval(parse(text = paste0("tastestrips$TasteStrip.",numstr,"response"))))
  
  hist(data, breaks = c(-0.5, 0.5, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5),
       main = "Taste Responses",
       xlab = "Response: Sweet, Sour, Salty, Bitter"
  )

  data <- na.omit(as.integer(eval(parse(text = paste0("tastestrips$TasteStrip.",numstr,"intensity")))))
  
  hist(data, breaks = c(-0.5, 0.5, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5),
       main = "All Intensity Responses",
       xlab = "Intensity Rating: 0, 1, 2, 3, 4, 5, 6, 7"
  )
medAll <- median(data)
```

### Intensity Responses to correct and incorrect responses
```{r, echo = FALSE, fig.height=2.8, fig.width=3.5}
  data <- na.omit(as.integer(eval(parse(text = paste0("tastestrips$TasteStrip.",numstr,"intensity[tastestrips$TasteStrip.",numstr,"score == 1]")))))
  
  hist(data, breaks = c(-0.5, 0.5, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5),
       main = "Corrected Responses - Intensity",
       xlab = "Intensity Rating: 0, 1, 2, 3, 4, 5, 6, 7"
  )
  ncorr <- length(data)
  medCorr <- median(data)
  meanCorr <- mean(data)
  stCorr <- sd(data)

  data <- na.omit(as.integer(eval(parse(text = paste0("tastestrips$TasteStrip.",numstr,"intensity[tastestrips$TasteStrip.",numstr,"score == 0]")))))
  
  hist(data, breaks = c(-0.5, 0.5, 1.5, 2.5, 3.5, 4.5, 5.5, 6.5, 7.5, 8.5, 9.5),
       main = "Incorrect Responses - Intensity",
       xlab = "Intensity Rating: 0, 1, 2, 3, 4, 5, 6, 7"
  )
  nincorr <- length(data)
  medinCorr <- median(data)
```  

For strip number `r i`, `r ncorr` responded correctly that the strip was `r tastelist[i]`

Their median estimated intensity was `r medCorr` - Mean: `r sprintf("%.1f",meanCorr)`, SD: `r sprintf("%.1f",stCorr)`

`r nincorr` responded incorrectly and they had a median intensity estimate of `r medinCorr`.
  
***
